A 30 Million Year Old Mini-Neptune in the Kepler Field

### 2021-05-18 paper/ms.tex
fine-tune del Lyr skyplot

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{
  {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored points are
  kinematically selected members of the $\delta$\,Lyr cluster (black points in
  Figure~\ref{fig:XYZvtang}).  Both Kepler (gray panels) and TESS (colored
  points) observed portions of the cluster.  Gray points are naked-eye stars
  ($m_{\rm V}<6.5$), three of which are annotated.  Kepler\,1627 (green star) was
  observed during the entirety of the Kepler mission, and has (so far) been observed
  for two lunar months by TESS.
  \label{fig:skychart}
  }
\end{figure*}

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{
  {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored
  points are kinematically selected members of the $\delta$\,Lyr
  cluster (black points in Figure~\ref{fig:XYZvtang}).  Both Kepler
  (gray panels) and TESS (colored points) observed portions of the
  cluster.  Naked-eye stars ($m_{\rm V}<6.5$) are shown in gray; four
  of them (orange points) have their names shown.  Kepler\,1627 (green
  star) was observed during the entirety of the Kepler mission, and
  has been observed  by TESS for two lunar months to date.
  \label{fig:skychart}
  }
\end{figure*}
